Gravitational Lens Recovery with \Glass: Measuring the mass profile and shape of a lens

### 2014-08-29 limits/ms.tex
Further fixes.

\item {\bf Model ensembles:} Model ensembles, exploring a diverse range of
    possible mass distributions that nonetheless all fit the data, are a way of
    combating the non-uniqueness of models.  Such ensembles are possible in
    parametric models \citep[e.g.,][]{1999AJ....118...14B,2010Sci...329..924J},
    and more recently with the Hubble Frontier Fields initiative
    \citep[e.g.,][]{}, but are more common in
    free-form models, where -- since such models are deliberately
    under-constrained -- they become vital
    \citep{2000AJ....119..439W,2009ApJ...690..154S,2012MNRAS.425.3077L}.

@@

\vspace{1mm}
\noindent
{\bf Regularisation priors}
\begin{enumerate}
\item The local gradient everywhere must point within $45^{\circ}$ of the center.
\item The azimuthally averaged density profile must have a slope everywhere $\le 0$.
\item The density is inversion symmetric.
\end{enumerate}
%
For typical lens data, the regularisation priors are very important for
creating physically sensible solutions. Prior (i) demands that the peak in the
mass density is at the centre of the mass map. Secondary `plateaus' in the mass
map are possible, but not secondary peaks. Note that this prior still
successfully allows merging galaxy systems to be correctly captured, provided
that the two galaxies are not equally dense in projection (see, for example the
\PixeLens{} model of the merger system B1608 in \citealt{2007ApJ...667..645R});
and for the successful detection of `meso-structure' in strong lensing galaxy
clusters \citep{2007ApJ...663...29S}. Prior (ii) is arguably a physical prior
since a negative azimuthally averaged density slope would be unstable
\citep[e.g.,][]{2008gady.book.....B}. Note that this prior does not preclude
successful modelling of mergers or substructure unless the total projected mass
in substructure is comparable to the projected mass of the host in an azimuthal
annulus \citep{2007ApJ...667..645R,2007ApJ...663...29S}. Prior (iii) is only
used for doubles that ought to be inversion symmetric and quads where inversion
symmetry is clear from the image configuration.

>>>>

\item {\bf Model ensembles:} Model ensembles, exploring a diverse range of
    possible mass distributions that nonetheless all fit the data, are a way of
    combating the non-uniqueness of models.  Such ensembles are possible in
    parametric models \citep[e.g.,][]{1999AJ....118...14B,2010Sci...329..924J,
    2014MNRAS.444..268R,2014arXiv1405.0222J,2014arXiv1405.0011C}, but are more
    common in free-form models, where -- since such models are deliberately
    under-constrained -- they become vital
    \citep{2000AJ....119..439W,2009ApJ...690..154S,2012MNRAS.425.3077L}.

@@

\vspace{1mm}
\noindent
{\bf Regularisation priors}
\begin{enumerate}
\item The local gradient everywhere must point within $45^{\circ}$ of the center.
\item The azimuthally averaged density profile must have a slope everywhere $\le 0$.
\item The density is inversion symmetric.
\end{enumerate}
%
For typical lens data, the regularisation priors are very important for
creating physically sensible solutions. Prior (i) demands that the peak in the
mass density is at the centre of the mass map. Secondary `plateaus' in the mass
map are possible, but not secondary peaks. Note that this prior still
successfully allows merging galaxy systems to be correctly captured, provided
that the two galaxies are not equally dense in projection (see, for example the
\PixeLens{} model of the merger system B1608 in \citealt{2007ApJ...667..645R});
and for the successful detection of `meso-structure' in strong lensing galaxy
clusters \citep{2007ApJ...663...29S}. Prior (ii) is arguably a physical prior
since a positive slope in the azimuthally averaged density profile would be unstable
\citep[e.g.,][]{2008gady.book.....B}. Note that this prior does not preclude
successful modelling of mergers or substructure unless the total projected mass
in substructure is comparable to the projected mass of the host in an azimuthal
annulus \citep{2007ApJ...667..645R,2007ApJ...663...29S}. Prior (iii) is only
used for doubles that ought to be inversion symmetric and quads where inversion
symmetry is clear from the image configuration.
